%% Emacshandbuch in deutsch
%%
%% Hauptseite für PDF
%%
%% $Revision: 1.3 $
%% $Id: ehbde_pdf.tex,v 1.3 2004/04/14 19:44:12 spica Exp $
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% ehbde_pdf.tex -> Mean File for the PDF-production
%
% Copyright (C) 2004 Joerg Meinhold 
%
% This document is free software; you can redistribute it and/or modify
% it under the terms of the GNU General Public License as published
% by the Free Software Foundation; either version 2 of the License.
%
% This document is distributed in the hope that it will be useful, but
% WITHOUT ANY WARRANTY; without even the implied warranty of MERCHANTABILITY
% or FITNESS FOR A PARTICULAR PURPOSE. See the GNU General Public License
% for more details.
%
% You should have received a copy of the GNU General Public License
% along with this document; if not, write to the Free Software Foundation,
% Inc., 59 Temple Place, Suite 330, Boston, MA 02111-1307, USA.
%
%
%
% ehbde_pdf.tex -> Haupt-Datei für die PDF-Erzeugung
%
% Copyright (C) 2004 Joerg Meinhold
% 
% Dieses Dokument ist freie Software. Sie können es unter den Bedingungen
% der GNU General Public License, wie von der Free Software Foundation
% veröffentlicht, weitergeben und/oder modifizieren, gemäß Version 2
% der Lizenz.
%
% Die Veröffentlichung dieses Dokuments erfolgt in der Hoffnung, daß
% es Ihnen von Nutzen sein wird, aber OHNE IRGENDEINE GARANTIE, sogar
% ohne die implizite Garantie der MARKTREIFE oder der VERWENDBARKEIT
% FÜR EINEN BESTIMMTEN ZWECK. Details finden Sie in der GNU General
% Public License.
%
% Sie sollten eine Kopie der GNU General Public License zusammen mit
% diesem Dokument erhalten haben. Falls nicht, schreiben Sie an die
% Free Software Foundation, Inc., 59 Temple Place, Suite 330, Boston,
% MA 02111-1307, USA.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt]{scrbook}
\usepackage{german}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{times}
\usepackage[pdftex]{graphicx}
\usepackage[backref]{hyperref}

\begin{document}

%% Titelseite

\title{GNU Emacs Handbuch\\
in deutsch\\
{\large Version 0.01}}

\author{\copyright {2004 Jörg Meinhold}}

\maketitle


%% Copyright-Vermerk

\chapter*{Copyright}

\begin{quote}
GNU Emacs - german Handbook about the editor GNU Emacs

Copyright (C) 2004 Joerg Meinhold

This document is freeware; you can redistribute it and/or modify it
under the terms of the GNU General Public License as published by
the Free Software Foundation; either version 2 of the License.

This document distributed in the hope that it will be useful, but
WITHOUT ANY WARRANTY; without even the implied warranty of MERCHANTABILITY
or FITNESS FOR A PARTICULAR PURPOSE. See the GNU General Public License
for more details.

You should have received a copy of the GNU General Public License
along with this document, if not, write to the Free Software Foundation,
Inc., 59 Temple Place, Suite 330, Boston, MA 02111-1307 USA
\\
\\

GNU Emacs Handbuch in deutsch

Copyright (C) 2004 Joerg Meinhold

Dieses Dokument ist freie Software. Sie können es unter den Bedingungen
der GNU General Public License, wie von der Free Software Foundation
veröffentlicht, weitergeben und/oder modifizieren, gemäß Version 2
der Lizenz.

Die Veröffentlichung dieses Programms erfolgt in der Hoffnung, daß
es Ihnen von Nutzen sein wird, aber OHNE IRGENDEINE GARANTIE, sogar
ohne die implizite Garantie der MARKTREIFE oder der VERWENDBARKEIT
FÜR EINEN BESTIMMTEN ZWECK. Details finden Sie in der GNU General
Public License.

Sie sollten eine Kopie der GNU General Public License zusammen mit
diesem Dokument erhalten haben. Falls nicht, schreiben Sie an die
Free Software Foundation, Inc., 59 Temple Place, Suite 330, Boston,
MA 02111-1307, USA.
\end{quote}


%% Inhaltsverzeichnis
\tableofcontents

\include{anhang}

\end{document}
